Procrastination and Dementia

### 2025-04-01 README.qmd
Update :bug:
Update readme

---
title: "Procrastination and Dementia"
format: 
  gfm: 
    wrap: preserve
    toc: true
  typst:
    toc: true
    toc-title: " "
    author:
    - name: Audrey L. Comstock
      affiliation: Arizona State University
      orcid: 0000-0003-1772-5350
      url: https://audreylcomstock.weebly.com/
      email: audrey.comstock@asu.edu
    - name: Andrew Heiss
      affiliation: Georgia State University
      orcid: 0000-0002-3948-3914
      url: https://www.andrewheiss.com
      email: aheiss@gsu.edu
    - name: Suparna Chaudhry
      affiliation: Lewis and Clark College
      orcid: 0000-0003-3506-7590
      url: https://www.suparnachaudhry.com/
      email: schaudhry@lclark.edu
---

@@

```{r setup, include=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)
```

::: {.content-visible when-format="markdown"}

---

[Cormac Monaghan](https://c-monaghan.github.io/)

---

:::

## Note on "crisp clam" project name

>>>>

---
format: gfm
---

@@

```{r setup, include=FALSE}
library(emoji)
```

##  `r emoji_glue(":potato::spiral_shell:")`: Note on "crisp clam" project name
